The first high-redshift changing-look quasars

### 2020-07-29 tex/MNRAS_submission/rv1/CIV_CLQs_rv1.tex
getting close to resubmisson

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_MBHvsREW_20200519.png}
   \vspace{-12pt}
   \caption[]{
     Colored density cloud shows virial black hole masses of
     $\approx$20,000 $z>1.5$ quasars from QSFit catalogue
     \citep{Calderone2017} compared to their \civ\ rest-frame equivalent
     widths (REWs).  Overplotted are the three high-redshift CLQs
     considered here: J1205+3422 (magenta), J1638+2827 (green), and
     J2228+2201 (cyan).  The symbol shapes indicate the observation epoch,
     with the first, second, and third epochs denoted by circles, squares,
     and diamonds, respectively. As per Table~\ref{tab:QSFit-results}, an
     asterisk in the inset box signifies that the \civ\ line for that
     quasar observation is very weak, likely making the associated
     estimates unreliable.}
   \label{fig:CIV_MBHvsREW}
\end{figure}

@@

For Equation~\ref{eqn:virial_masses}., \citet{VestergaardPeterson2006}
measure $\gamma=0.53$ and the offset as $a=0.660$, and these estimates
are widely adopted \citep[e.g.,][]{Shen2011, Chen2019, Yao2019}.
\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
both the DR7 Quasar catalog and DR12 Quasar catalog.
\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
$z>1.3$ quasars that show significant lag measurements,
and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
their highest-confidence objects. }

@@

%%
%%  These values are generated using the 
%%
\begin{table}
  \centering
  \begin{tabular}{l c cc l}
    \hline
    \hline
                      &                 &                                     &                               & \\
Object            & MJD          &  $\log (M/M_{\odot})$  & log($L_{\rm bol}$)    &  $\eta_{\rm Edd}$  \\
                      &                 &                                     &                               & \\
    \hline
\multirow{4}{*}{J1205+3422} & 53498          &   9.49$^{\dagger }$   &   47.22$^{\dagger }$  & $-$0.38$^{\dagger }$   \\
                                             &  53498        &   9.39                       &   47.20                      & $-$0.61   \\
                                             & $^{*}$58538  &   9.78                       &  46.03                      & $-$1.84 \\  
                                             & 58693            &  9.38                       &  46.54                      &  $-$0.95  \\                    
    \hline
\multirow{5}{*}{J1638+2827} & 54553            & 8.74$^{\dagger }$     &  46.17$^{\dagger }$   & $-$0.68$^{\dagger }$  \\
                                              & 54553            & 8.84                        &   46.19    & $-$0.75  \\
                                             & 55832           & 9.13$^{\ddagger }$  &    46.72    & $-$0.72$^{\ddagger }$  \\      
                                             & 55832          & 8.80                         &   45.99    & $-$0.91 \\     
                                             & 58583           & 9.01                        &    46.52    & $-$0.60   \\
    \hline
\multirow{4}{*}{ J2228+2201} & 56189         & 8.73$^{\ddagger }$ & 46.23$^{\ddagger }$  &  $-$1.32$^{\ddagger }$ \\
                                              &  56189      & 8.70                       & 45.51                        &  $-$1.29 \\
                                              & 56960         &  9.39                      &  46.54                        & $-$0.95  \\      
                                              & 58693          &  8.97                      & 46.03                         &  $-$1.05 \\
    \hline
    \hline
  \end{tabular}
  \caption{The \civ\ virial mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars.
    The virial masses are calculated using the measured 1450\AA\ monochromatic luminosites and \civ\ FWHM
    as reported by QSFit, with $^{*}$ designating low SNR line measurements.
        $\dagger$Values from the \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\ddagger$Values from the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
    The Eddington luminosity is 
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}

@@

In standard \citet{SS73} thin disk models, large changes in the
continuum flux are not permitted over short timescales due to the
relatively long viscous time associated with such disks. Given the
observed short timescale continuum variations, we must consider more
complex models. We note that two of our sources (J1205+3422 and
J2228+2201) have \civ\ EW and continuum luminosity changes which fall
comfortably along a line, implying their variation is consistent with
an intrinsic Baldwin effect (see Figure~\ref{fig:CIV_Baldwin}).
%%
{\bf The light-crossing time of the region that produces the \civ\ line is substantial,
which translates into a delay between the variations of the continuum and
the \civ\ line, and a smoothing of the light curve of the latter.
%%
Thus, if the excitation of the \civ\ line is driven by the changes in the
continuum, the excited gas cannot reach an equilibrium
excitation state as quickly as the continuum changes.}
This makes the slope of the intrinsic Baldwin effect greater than that
of the overall ensemble slope, which is derived from many single-epoch
observations, the majority of which are assumed to be in equilibrium.
{\bf \citet{Grier2019}, }

@@

\begin{figure*}
  \centering
  \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/MJD_vs_Eddington_20191211}
  \vspace{-12pt}
  \caption[]{Eddington ratios of the three \civ\ CLQs.  Grayscale gives the
    Eddington ratio ranges for quasars from SDSS \citet[][]{Shen2011} and
    BOSS \citep[][]{Kozlowski2017}.  Symbols as in
    Figure~\ref{fig:CIV_MBHvsREW}.  The red region ($L / L_{\rm Edd}
    \approx 0.02 \pm 0.01$; $\eta_{\rm Edd} = -1.7 \pm 0.13$) is the
    transition accretion rate suggested by \citet{NodaDone2018}.  A
    ``High/Soft State'' with $\eta_{\rm Edd} \geq -1$ and a a ``Low/Hard
    State'' with $\eta_{\rm Edd} \leq -2$ are indicated with dashed lines
    and arrows.}
  \label{fig:Eddington_ratios}
\end{figure*}

@@

Apart from J1205+3422 on MJD 58538, we see all the \civ\ CLQ epochs
are above $L / L_{\rm Edd} \sim 5$\%. As we have noted throughout, the
spectrum for J1205+3422 on MJD 58538 has low SNR, so while this object
could well have entered a `low-state', this is difficult to
conclusively confirm.  Nevertheless, and taking the J1205+3422
spectrum at face-value, we note that all the \civ\ CLQs are well above
$\sim1\%$ in Eddington luminosity and thus the suggested ``Low/Hard
State'' boundary.

@@

\begin{itemize}
\item SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting
  behaviour in their observed optical light curves, and subsequent
  spectroscopy shows significant changes in the \civ\ broad emission
  line, with both line collapse and emergence being displayed on
  rest-frame timescales of $\sim 240-1640$~days.
\item Where observed, the profile of the Ly$\alpha$/\nv emission complex
  also changes, and there is tentative evidence for changes in the \mgii\
  line.
\item Although line measurements from the three quasars show large changes
  in the \civ\ line flux-line width plane, the quasars are not seen to
  be outliers when considered against the full quasar population
  in terms of (rest-frame) EW and FWHM properties.
\item 
  We put these observations in context with recent ``state-change''
  models, and note that with the exception of the low SNR spectrum of
  J1205+3422 on MJD 58538, even in their low state, 
  the \civ\ CLQs are above $\sim5$\% in Eddington luminosity. 
\end{itemize}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_MBHvsREW_20200710.png}
   \vspace{-12pt}
   \caption[]{
     Virial black hole masses of 
     $\approx$20,000 $z>1.5$ quasars from QSFit catalogue
     \citep{Calderone2017} compared to their \civ\ rest-frame equivalent
     widths (REWs).  Overplotted are the three high-redshift CLQs
     considered here: J1205+3422 (magenta), J1638+2827 (green), and
     J2228+2201 (cyan).  The symbol shapes indicate the observation epoch,
     with the first, second, and third epochs denoted by circles, squares,
     and diamonds, respectively. As per Table~\ref{tab:QSFit-results}, an
     asterisk in the inset box signifies that the \civ\ line for that
     quasar observation is very weak, likely making the associated
     estimates unreliable.}
   \label{fig:CIV_MBHvsREW}
\end{figure}

@@

For Equation~\ref{eqn:virial_masses}, \citet{VestergaardPeterson2006}
measure $\gamma=0.53$ and the offset as $a=0.660$, and these estimates
are widely adopted \citep[e.g.,][]{Shen2011, Chen2019, Yao2019}.
\citet{Kozlowski2017} have similar values \citet{VestergaardPeterson2006} , with $(a,\gamma)=(0.64, 0.53)$,
but note there is a problem with the FWHMs for \civ\ for those quasars that are reported in
both the DR7 Quasar catalog and DR12 Quasar catalog.
\citet{Grier2019} measure a slope of $\gamma=0.51\pm0.05$ for their sample of high-redshift
$z>1.3$ quasars that show significant lag measurements,
and  $\gamma=0.52\pm0.04$ for their ``gold sample'' of 16 of
their highest-confidence objects. }

@@

%%
%%  These values are generated using the 
%%
\begin{table}
  \centering
  \begin{tabular}{l c cc l}
    \hline
    \hline
                      &                 &                                     &                               & \\
Object            & MJD          &  $\log (M/M_{\odot})$  & log($L_{\rm bol}$)    &  $\eta_{\rm Edd}$  \\
                      &                 &                                     &                               & \\
    \hline
\multirow{4}{*}{J1205+3422} & 53498          &   9.49$^{\dagger }$   &   47.22$^{\dagger }$  & $-$0.38$^{\dagger }$   \\
                                             &  53498        &   9.39                       &   47.20                      & $-$0.29   \\
                                             & $^{*}$58538  &   9.78                       &  46.03                      & $-$1.84 \\  
                                             & 58693            &  9.38                       &  46.54                      &  $-$0.95  \\                    
    \hline
\multirow{5}{*}{J1638+2827} & 54553            & 8.74$^{\dagger }$     &  46.17$^{\dagger }$   & $-$0.68$^{\dagger }$  \\
                                              & 54553            & 8.84                        &   46.19    & $-$0.75  \\
                                             & 55832           & 9.13$^{\ddagger }$  &    46.72    & $-$0.72$^{\ddagger }$  \\      
                                             & 55832          & 8.80                         &   45.99    & $-$0.91 \\     
                                             & 58583           & 9.01                        &    46.52    & $-$0.60   \\
    \hline
\multirow{4}{*}{ J2228+2201} & 56189         & 8.73$^{\ddagger }$ & 46.23$^{\ddagger }$  &  $-$1.32$^{\ddagger }$ \\
                                              &  56189      & 8.70                       & 45.51                        &  $-$1.29 \\
                                              & 56960         &  9.39                      &  46.54                        & $-$0.95  \\      
                                              & 58693          &  8.97                      & 46.03                         &  $-$1.05 \\
    \hline
    \hline
  \end{tabular}
  \caption{The \civ\ virial mass estimates, bolometric luminosities and Eddington ratios for the
    three quasars.
    The virial masses are calculated using the measured 1450\AA\ monochromatic luminosites and \civ\ FWHM
    as reported by QSFit, with $^{*}$ designating low SNR line measurements.
        $\dagger$Values from the \citet{Shen2011} SDSS DR7 Quasar catalog.
    $\ddagger$Values from the \citet{Kozlowski2017} SDSS-III BOSS DR12 quasar catalog.
    The Eddington luminosity is 
    $L_{\rm Edd} = 1.26\times10^{38} (M_{\rm BH}/M_{\odot})$ erg s$^{-1}$
    and $\eta_{\rm Edd}$ is the log of the Eddington ratio.}
\label{tab:Eddington_ratios} 
\end{table}

@@

In standard \citet{SS73} thin disk models, large changes in the
continuum flux are not permitted over short timescales due to the
relatively long viscous time associated with such disks. Given the
observed short timescale continuum variations, we must consider more
complex models. We note that two of our sources (J1205+3422 and
J2228+2201) have \civ\ EW and continuum luminosity changes which fall
comfortably along a line, implying their variation is consistent with
an intrinsic Baldwin effect (see Figure~\ref{fig:CIV_Baldwin}).
%%
{\bf The light-crossing time of the region that produces the \civ\ line is substantial,
which translates into a delay between the variations of the continuum and
the \civ\ line, and a smoothing of the light curve of the latter.
%%
Thus, if the excitation of the \civ\ line is driven by the changes in the
continuum, the excited gas cannot reach an equilibrium
excitation state as quickly as the continuum changes.}
This makes the slope of the intrinsic Baldwin effect greater than that
of the overall ensemble slope, which is derived from many single-epoch
observations, the majority of which are assumed to be in equilibrium.

@@

\begin{figure*}
  \centering
  \includegraphics[width=14.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/MJD_vs_Eddington_20200710}
  \vspace{-12pt}
  \caption[]{Eddington ratios of the three \civ\ CLQs.  Grayscale gives the
    Eddington ratio ranges for quasars from SDSS \citet[][]{Shen2011} and
    BOSS \citep[][]{Kozlowski2017}.  Symbols as in
    Figure~\ref{fig:CIV_MBHvsREW}.  The red region ($L / L_{\rm Edd}
    \approx 0.02 \pm 0.01$; $\eta_{\rm Edd} = -1.7 \pm 0.13$) is the
    transition accretion rate suggested by \citet{NodaDone2018}.  A
    ``High/Soft State'' with $\eta_{\rm Edd} \geq -1$ and a a ``Low/Hard
    State'' with $\eta_{\rm Edd} \leq -2$ are indicated with dashed lines
    and arrows.}
  \label{fig:Eddington_ratios}
\end{figure*}

@@

Apart from J1205+3422 on MJD 58538, we see all the \civ\ CLQ epochs
are above $L / L_{\rm Edd} \sim$5\%. As we have noted throughout, the
spectrum for J1205+3422 on MJD 58538 has low SNR, so while this object
could well have entered a `low-state', this is difficult to
conclusively confirm.  Nevertheless, and taking the J1205+3422
spectrum at face-value, we note that all the \civ\ CLQs are above
$\sim$1\% in Eddington luminosity and thus the suggested ``Low/Hard
State'' boundary.

@@

\begin{itemize}
\item SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting
  behaviour in their observed optical light curves, and subsequent
  spectroscopy shows significant changes in the \civ\ broad emission
  line, with both line collapse and emergence being displayed on
  rest-frame timescales of $\sim 240-1640$~days.
\item Where observed, the profile of the Ly$\alpha$/\nv emission complex
  also changes, and there is tentative evidence for changes in the \mgii\
  line.
\item Although line measurements from the three quasars show large changes
  in the \civ\ line flux-line width plane, the quasars are not seen to
  be outliers when considered against the full quasar population
  in terms of (rest-frame) EW and FWHM properties.
\item 
  We put these observations in context with recent ``state-change''
  models, and note that with the exception of the low SNR spectrum of
  J1205+3422 on MJD 58538, even in their low state, 
  the \civ\ CLQs are above $\sim$5\% in Eddington luminosity. 
\end{itemize}
